Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-18 mpaper/paper.tex
Second round of plots for describing the part that doesn't work

\documentclass{mpaper}
\usepackage{bm}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{thmtools, thm-restate}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{tikz}
\usepackage{layouts}

@@

\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\adj}{adj}
%\DeclareMathOperator{\dett}{det}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

% Maybe?
%\subsection{Implementation}

@@

 % TODO: need to redo this to get better labels, more precision, wider range of values
\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{elbo_contour_plots}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{elbo_over_gamma}
  \caption{Changes in $\mathcal{L}$ as a function of $\bm\mu$, where $\mu_1 =
    \mu_2 = \mu_3$, and $\gamma = 0, 0.1, \dots, 0.9$. Each of the ten curves
    plots a different value of $\gamma$, ranging from $0$ in dark blue to $0.9$
    in dark red.}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{ELBO_and_gradient_over_B}
  \caption{ELBO in blue, derivative in red. The first row is for diagonal values
  of B, the second row is for non-diagonal values.}
\end{figure*}

How well does the variance prediction work? It doesn't, but why?
TODO: Sage should consider 3x3 matrices
TODO: 4 plots---two my MATLAB, two my Sage; two for B[1, 1], two for B[2, 1].
The MATLAB plots show E[v] and dE[v]/dB, the Sage plots show q(u) and
dq(u)/dB. Function in blue, derivative in red, over a range of values.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{sage1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{sage2}
\end{figure}

% How does policy depend on rewards? Choose state and action, generate an array
% of contour plots showing the probability of taking that action in an optimal policy
Observation from a plot not worth including here. The policy behaves as
expected: if we fix $r(s_1)$, $\pi(s_1, a_1)$ increases with higher $r(s_2)$ as
well as lower $r(s_3)$ values.

>>>>

\documentclass{mpaper}
\usepackage{bm}
\usepackage{bbm}
\usepackage{mathtools}
\usepackage{thmtools, thm-restate}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{tikz}
\usepackage{layouts}
%\usepackage{subcaption}

@@

\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\adj}{adj}
\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

@@

\begin{figure*}
  \centering
  \begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=\columnwidth]{sage1}
    \includegraphics[width=\columnwidth]{sage2}
  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=\columnwidth]{elbo_over_B_short}
  \end{minipage}
  \caption{How a well-defined problem with a correct solutions becomes a
    well-defined problem with an incorrect solution. In each plot, the function
    we are trying to optimise is in blue, and its derivative is in red. The
    plots on the left are for $q(\mathbf{u})$ and its derivatives with respect
    to $B_{1,1}$ (at the top) and $B_{2,1}$ (at the bottom), whereas the plots
    on the right are for $\mathbb{E}[v]$ and its corresponding derivatives.}
\end{figure*}
% TODO: describe the figure

% TODO: evaluate by setting dE[v]/dB to zero
% How does policy depend on rewards? Choose state and action, generate an array
% of contour plots showing the probability of taking that action in an optimal policy

% Observation from a plot not worth including here. The policy behaves as
% expected: if we fix $r(s_1)$, $\pi(s_1, a_1)$ increases with higher $r(s_2)$ as
% well as lower $r(s_3)$ values.
